Precision calculations for cosmic shear

### 2017-02-09 limber2.tex
added empty conclusions.tex file will now fill it
MK small changes
Added author list, addresses and the acks that I know about

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author[M.~Kilbinger et~al.]
 {
  \parbox[h]{\textwidth}
  {
      Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
      %Catherine Heymans,
      %Peter Schneider,
      %Shahab Joudaki,
      %Marika Asgari,   % note that we'll worry about order at the end - Marika and Shahab put a lot of work into the comment paper, so we might just want to go alpha
      and other members of CFHTLenS and KiDS
      $\ldots$,
  }
  % 
  \vspace*{10pt} \\
  \hspace{-.1cm}$^1$ CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
  \hspace{-.1cm}$^2$ Institut d'Astrophysique de Paris, UMR7095 CNRS,
           Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris,
           France \\
 }

\voffset-0.50in

@@

\maketitle

@@

\begin{abstract}

@@

\section{Conclusions}

@@

The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful discussions.

@@

    \caption{Relative differences in percentage of spherical first- and second-order Limber
    shear power spectra with respect to the full projection
    as function of wave mode $\ell$, see Table \ref{tab:cases}. The redshift distribution
    and the cosmological parameters (see text) are chosen to match
    \citet{vande2012}, see their Fig.~7.3 for comparison.
    }

>>>>

@@

\input{authors.tex}

@@

\begin{document}
\setlength{\voffset}{-12mm}

@@

\maketitle
\begin{abstract}

@@

\section{Conclusions}
\input{conclusions.tex}

@@

The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful discussions.
This work was financially supported by the DFG (Emmy Noether grants Hi 1495/2-1 and SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), NSERC and CIfAR.

\ch{Check your acknowledgements}

@@

    \caption{Relative differences in percentage of spherical first- and second-order Limber
    shear power spectra with respect to the full projection
    as function of wave mode $\ell$, see Table \ref{tab:cases}. The redshift distribution
    is a single source plane at $z_{\rm S}=1$, and the cosmological parameters (see text) are chosen to match
    \citet{vande2012}, see their Fig.~7.3 for comparison.
    }
